Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-06-20 outputs/paper/paper.qmd
Notes in paper.qmd
Update paper.qmd

---
title: "Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area."
author: "Sarah Mansoor"
thanks: "Code and data are available at: https://github.com/sarahmansoorr/SUDS2022"
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pdf
editor: visual
abstract: ""
toc: true
bibliography: references.bib
---

@@

@@

@@

## Visualizing the Data and the Implications

@@

>>>>

---
#### Preamble ####
title: "Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area."
author: "Sarah Mansoor"
email: "sarah.mansoor@mail.utoronto.ca"
thanks: "Code and data are available at: https://github.com/sarahmansoorr/SUDS2022"
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pdf
editor: visual
abstract: "The growing impact of climate change in Canada demonstrates a clear and current threat to human health. These threats are becoming revealed in Canada as the country continues to face the consequences of warming almost at twice the global rate. In this report, I will explore how tempreture increases, lower air quality relate to a rise in threats to human healht in Toronto. Once the data for this research was collected, the data cleaning process begun which entailed of using packages in R like tidyverse, janitor, dplyr, …. Duplicate and irrelevant observations were removed, as well as unwanted outliers. The process was complete once the data was correct, consistent and usable. "
toc: true
bibliography: references.bib
---

@@

Why do we care?

What is in this paper?

Results?

@@

table of variables used?

@@

## Visualizing the Data and the Implications (needs to be reworded)

use other graphs beside boxplot. log scales. (dotpoint, barchart, etc)

avoid drastic, dramatic, etc

@@

need updated data?
